---
title: "EssentialJSONSerializer (R package)"
author: "Jellen Vermeir"
date: "March 20, 2019"
output: rmarkdown::github_document
---

The intention of the package fuctionality is to (de)serialize language specific complex objects towards generic 
JSON-datatype objects. The JSON conversion allows for flexible cross language communication when the package is implemented
across different languages. This package provides an R implementation of the (de)serialization functionality.

the package can be installed from github by using the ```devtools``` utility:

```{r eval=FALSE}
# install.packages("devtools") # if devtools currently not installed
devtools::install_github("VermeirJellen/essentialjsonserializer_r")
```

## JSON (de)serialization of complex R-objects.

Currently, 6 generic complex JSON-datatypes are provided. Corresponding R-mappings are defined as follows:

* JSON **datetime**         - maps to R ```POSIXct``` objects
* JSON **timeseries**       - maps to R 1-dimensional ```xts``` objects
* JSON **timeseries_n_dim** - maps to R n-dimensional ```xts``` objects (n > 1)
* JSON **series**           - maps to R 1-dimensional ```dataframe``` objects
* JSON **dataframe**        - maps to R n-dimensional ```dataframe``` objects (n > 1)
* JSON **matrix**           - maps to R ```matrix``` objects


The package provides the user with the ```EssentialJSONSerializer``` reference class. Following functions
are provided:

* ```RToList```: Convert complex R structures to a generic datatype list structure.
* ```RToJSON```: Convert complex R structures to a generic datatype JSON structure.
* ```RFromList```: Convert generic datatype list structure to complex R-specific objects.
* ```RFromJSON```: Convert generic datatype JSON structure to complex R-specific objects.


## Examples

#### **EssentialJSONSerializer Object Construction**

```{r message=FALSE}
Sys.setenv(tz="UTC")
library(essentialjsonserializer)
essential.serializer <- EssentialJSONSerializer$new()
```


#### **list**

Serialize:

```{r}
list.input <- list(c(1, 2, 3, 4, 5), 
                   c(6, 7, 8), list(c(1, 2, 3)))
list.json <- essential.serializer$RToJSON(list.input)
cat(list.json)
```
  
Deserialize:

```{r}
list.json.revert <- essential.serializer$RFromJSON(list.json)
```



#### **datetime**

Serialize:

```{r}
datetime.input  <- as.POSIXct(Sys.time(), tz="UTC")
datetime.json   <- essential.serializer$RToJSON(datetime.input)
cat(datetime.json)
```

Deserialize:

```{r}
datetime.json.revert <- essential.serializer$RFromJSON(datetime.json)
datetime.json.revert
```



#### **datetime (nested)**

Serialize:

```{r}
datetime.nested.input <- list(input.1 = datetime.input, 
                              input.2 = as.POSIXct(Sys.Date(), tz="UTC"))

datetime.nested.json    <- essential.serializer$RToJSON(datetime.nested.input)
cat(datetime.nested.json)
```

Deserialize:

```{r}
datetime.nested.json.revert <- essential.serializer$RFromJSON(datetime.nested.json)
datetime.nested.json.revert
```

#### **timeseries**

Serialize:

```{r}
timeseries.input  <- xts::xts(matrix(c(5, 7, 9, NA), ncol=1), 
                              order.by = c(as.POSIXct("2017-01-01", tz="UTC"),
                                        as.POSIXct("2017-01-02", tz="UTC"),
                                        as.POSIXct("2017-01-03", tz="UTC"),
                                        as.POSIXct("2017-01-04", tz="UTC")))
names(timeseries.input) <- "name_series"

timeseries.json    <- essential.serializer$RToJSON(timeseries.input)
cat(timeseries.json)
```

Deserialize:

```{r}
timeseries.json.revert <- essential.serializer$RFromJSON(timeseries.json)
timeseries.json.revert
```


#### **timeseries_n_dim**

Serialize:

```{r}
timeseriesndim.input  <- xts:::xts(matrix(c(5, 7, 9, 12, 15, 19), ncol=2), 
                             order.by = c(as.POSIXct("2017-01-01", tz="UTC"),
                                          as.POSIXct("2017-01-02", tz="UTC"),
                                          as.POSIXct("2017-01-03", tz="UTC")))
names(timeseriesndim.input) <- c("name_series_1", "name_series_2")

timeseriesndim.json <- essential.serializer$RToJSON(timeseriesndim.input)
cat(timeseriesndim.json)
```

Deserialize:

```{r}
timeseriesndim.json.revert <- essential.serializer$RFromJSON(timeseriesndim.json)
timeseriesndim.json.revert
```

#### **timeseries_n_dim (nested)**

Serialize:

```{r}
timeseries.nested.input <- list(ts1 = timeseries.input, 
                                ts2 = timeseriesndim.input)
timeseries.nested.json <- essential.serializer$RToJSON(timeseries.nested.input)
cat(timeseries.nested.json)
```

Deserialize:

```{r}
timeseries.nested.json.revert <- essential.serializer$RFromJSON(timeseries.nested.json)
timeseries.nested.json.revert
```


#### **series**

Serialize:

```{r}
series.input        <- data.frame(c(1, 2, 3, 4), 
                                  row.names = c("one", "two", "three", "four"))
names(series.input) <- "only_column"

series.json  <- essential.serializer$RToJSON(series.input)
cat(series.json)
```

Deserialize:

```{r}
series.json.revert <- essential.serializer$RFromJSON(series.json)
series.json.revert
```


#### **dataframe**

Serialize:

```{r}
dataframe.input        <- data.frame(c(1, 2, 3, 4), c(4, 5, 6, 7),
                                     row.names = c("one", "two", "three", "four"))
names(dataframe.input) <- c("first_col", "second_col")

dataframe.json <- essential.serializer$RToJSON(dataframe.input)
cat(dataframe.json)
```

Deserialize:

```{r}
dataframe.json.revert <- essential.serializer$RFromJSON(dataframe.json)
dataframe.json.revert
```


#### **matrix**

Serialize:
```{r}
matrix.input <- matrix(c(1, 2, 3, 4, 5, 6), ncol = 2, byrow = TRUE)

matrix.json <- essential.serializer$RToJSON(matrix.input)
cat(matrix.json)
```

Deserialize:

```{r}
matrix.json.revert <- essential.serializer$RFromJSON(matrix.json)
matrix.json.revert
```

#### **nested structure**

Serialize:
```{r}
r.input <- list(list.input           = list.input,
                datetime.input       = datetime.input,
                datetime.nested      = datetime.nested.input,
                timeseries.input     = timeseries.input,
                timeseriesndim.input = timeseriesndim.input,
                series.input         = series.input,
                dataframe.input      = dataframe.input,
                matrix.input         = matrix.input,
                timeseries.nested    = timeseries.nested.input)

                
r.json <- essential.serializer$RToJSON(r.input)
cat(r.json)
```

Deserialize:
```{r}
r.json.revert <- essential.serializer$RFromJSON(r.json)
r.json.revert
```


## Donations

If you find this software useful and/or you would like to see additional extensions, feel free to donate some btc:

 - BTC: 3NmxUnuK8ZqAszzFzcpBerKsy4ajQpb8mi
 
## Licensing

Copyright 2019 Essential Data Science Consulting ltd. ([EssentialDataScience.com](http://essentialdatascience.com "EssentialDataScience") / jellenvermeir@essentialdatascience.com).
This software is copyrighted under the MIT license: View added [LICENSE](./LICENSE) file.